\section{Introduction}
%TODO Renan
% 1 page

Hydropower has an important share in the global electricity production, and
will continue to be a major source of renewable power-generation technology
\cite{iea}. Large hydropower projects have typically an average maintenance
cost of 2\% to 2.5\% of the investment cost per kW \cite{irena}, and a major
concern is the state of the runner's blades, which suffer cavitation and
abrasion phenomena. The erosion can lead to water flow instability, excessive
vibrations and turbine efficiency reduction \cite{goldemberg2007energia}, thus
hard coating techniques by thermal aspersion are used to greatly increase the
life cycle of runner's blades~\cite{krella2011new}.

The use of robotics for in situ maintenance, and repair operations in
hydropower plants could greatly improve efficiency, health and safety, while
decreasing operational and logistics costs~\cite{hazel2012field}. The working
conditions on hydropower turbine installations are unfriendly, the atmospheric
conditions, high temperatures and humidity, and constrained space are
unfavorable to human operation. Also, some tasks, as the hard coating
procedure, requires a robotic system due to high precision, speed, and the
usage of hazardous substances (as propane and others).

In the specific case of Brazil, hydropower is the most important
power-generation technology. To support future economic growth, Brazil has
invested in additional hydroelectric facilities, for instance, the
14,000-megawatt Belo Monte dam along the Xingu River~\cite{eia}, and Jirau dam
along the Madeira river. At the latter, the number of suspended particles that
the river carries intensifies the abrasion phenomena, thus regular maintenance
is needed.

Currently, the majority of the robotic systems for in situ hydropower
maintenance are used for repair tasks, such as inspection, welding, and
grinding. 

Some examples found in the literature are:

The Roboturb~\cite{roboturb} is a robotic manipulator to perform erosion
inspection, and welding on damaged runner's blades. It is composed of six
revolution joints and one prismatic joint coupled to a flexible rail, which may
be shaped and then fixed to the blade surface by a passive system of suction cups.

The Scompi~\cite{scompi} is a multipurpose manipulator, designed to
perform repairs on \textit{Francis} type turbines, as welding and grinding. It
is composed of five revolution joints (manipulator) and one prismatic joint
coupled to curved rails.

\textit{The Climber}~\cite{icm} is an inspection robot for wind and
hydroelectric turbines, to perform coating removal, surface cleaning and
coating application. It is a climbing robot with pneumatic adhesion and
locomotion by tracks.

In this paper, we present a general overview of the EMMA robot, and a detailed
description of the mechanics, manipulator analysis, and calibration.

EMMA is a robotic system to perform \textit{in situ} hydropower runner's
blade hard coating, being developed by COPPE/UFRJ in collaboration with Agência
Nacional de Energia Elétrica (ANEEL) and Energia Sustentável do Brasil (ESBR). The system
is composed of an industrial manipulator that moves on a customized rail base, a
3D laser scanner for mapping, and sensors for positioning feedback. The
system will autonomously operate in a confined space, moves on a sloping
and slippery environment through a rail, identify the runner's blades, calibrate
its position, generates the path planning and performs the hard coating. The
project aims to significantly reduce the downtime for hard coating process.

%This text is organized as follows: a general overview of the robot and its main
%challenges are presented in Section \ref{sec:general_overview}, detailed
%descriptions of the embedded electronics, the vehicle support system, power
%supply system, and software architecture are taken in
%Sections \ref{sec:electronics_overview}, \ref{sec:powersupply_overview}, and
%\ref{sec:software} respectively.
%In Section \ref{sec:results}, preliminary results are shown, and concluding
%remarks are drawn in Section \ref{sec:conclusions}.

\begin{comment}
require stoppage of the turbine, removing the
blades, positioning the blades for coating, coating application, turbine assembling, and recalibration. The downtime to perform all
maintenance can take up to two months, meaning a huge loss in power generation.
\end{comment}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{comment}

The efficiency of a hydraulic turbine is related at some extend to the hydraulic
profile of the runner blades and its degradation is mainly due to two
phenomena: cavitation and abrasion. As a protective measure, the blades are
hardcoated by a process called HVOF (High velocity oxy-fuel coating spraying),
which mitigate the damage caused by the aforementioned effects, but has to be
reapplied periodically.

The hardcoating process can take up to two months per turbine, including turbine
disassemble, blade's hardcoating on a specifically designed environment and
following remounting and calibration.

Aiming to reduce the downtime assossiated for the hardcoating process, robotic
\textit{in situ} solutions, i.e. inside the runner environemnt, consisting of a
insdustrial robotic arm mounted over a customized base are scrutinized. This is
the main objetive of the EMMA project, a R\&D project by Fundação Coordenação
de Projetos, Pesquisas e Estudos Tecnológicos (COPPETEC), in partnership with
Rijeza company, Agência Nacional de Energia Elétrica (ANEEL) and Energia
Sustentável do Brasil (ESBR).


The workflow for the \textit{in situ} hardcoating can be thought as a
sequence of 4 minor jobs:
Enter the runner area with the robot; Move the robot and anchor it in some
suitable positions near the blade to be hardcoated; Calibrate the robot, in the
sense of identifying the relative positions of the robot, blade and the rest of
the environment; And finally, check if the the robot's arm can cover the whole
blade.

The following sections explore the developments on the EMMA project, they are
organized so to mimic the workflow:
section 2 exposes the ideas for the customized base and related logistics;
section 3 describes the calibration process which has to be done once the robot
is well placed, but before it's able to start coating; section 4 explore the
robot arm's limitations for performing the hardcoating; And lastly section 5
concludes and discusses the future steps for the EMMA project.
\end{comment}